---
title: "Learning Curve Report"
output: html_document
params: 
  n: character
  Tbl: data.frame
  dtlong: data.frame
  SetTbl: data.frame
  indColor: NA
  StudentName: character
  DF2: data.frame
author: "`r params$StudentName`"

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Lego Set Color 

```{r echo=FALSE}
params$n
```

## Timing Data Table

```{r echo=FALSE}
params$Tbl
```


## Learning Curve Plots
###**Individual Graphs**

```{r echo=FALSE,warning=FALSE,message=FALSE}
   
ggplot(data =params$Tbl,aes(params$Tbl[,1],params$Tbl[,2]))+
     geom_point(color = as.character(params$n))+
     geom_line()+
     ggtitle(paste(names(params$Tbl)[2]))+
     theme(plot.title = element_text(size=20, hjust = .5))+
     xlab("Trials")+
     ylab("Duration")+
     scale_y_continuous(expand=c(.1,.1),limits = c(min(params$Tbl[,2]),NA))+
     scale_x_continuous(breaks = seq(1,16,1))+
     stat_smooth(method = 'nls',
                 formula = 'y~a*x^b',
                 method.args = list(start= c(a = 1,b=1)),
                 se=FALSE,
                 fullrange = TRUE,
                 n=100,
                 color="magenta")
```


```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(data =params$Tbl,aes(params$Tbl[,1],params$Tbl[,3]))+
     geom_point(color = as.character(params$n))+
     geom_line()+
     ggtitle(paste(names(params$Tbl)[3]))+
     theme(plot.title = element_text(size=20, hjust = .5))+
     xlab("Trials")+
     ylab("Duration")+
     scale_y_continuous(expand=c(.1,.1),limits = c(min(params$Tbl[,3]),NA))+
     scale_x_continuous(breaks = seq(1,16,1))+
     stat_smooth(method = 'nls',
                 formula = 'y~a*x^b',
                 method.args = list(start= c(a = 1,b=1)),
                 se=FALSE,
                 fullrange = TRUE,
                 n=100,
                 color="magenta")
```


```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(data =params$Tbl,aes(params$Tbl[,1],params$Tbl[,4]))+
     geom_point(color = as.character(params$n))+
     geom_line()+
     ggtitle(paste(names(params$Tbl)[4]))+
     theme(plot.title = element_text(size=20, hjust = .5))+
     xlab("Trials")+
     ylab("Duration")+
     scale_y_continuous(expand=c(.1,.1),limits = c(min(params$Tbl[,4]),NA))+
     scale_x_continuous(breaks = seq(1,16,1))+
     stat_smooth(method = 'nls',
                 formula = 'y~a*x^b',
                 method.args = list(start= c(a = 1,b=1)),
                 se=FALSE,
                 fullrange = TRUE,
                 n=100,
                 color="magenta")
```


###**Combined Graphs**

```{r echo=FALSE,warning=FALSE,message=FALSE}
   ggplot(data = params$dtlong,aes(Trial,Duration,color=Lego))+
     geom_point(aes(shape = Lego),color = as.character(params$n))+
     geom_line()+
     ggtitle(paste(params$n," Set: Data"))+
     theme(plot.title = element_text(size=20, hjust = .5))+
     xlab("Trials")+
     scale_y_continuous(expand=c(.1,.1),limits = c(min(params$dtlong[,3]),NA))+
     scale_x_continuous(breaks = seq(1,16,1))
```


```{r echo=FALSE,warning=FALSE,message=FALSE}
if(sum(params$Tbl[,2])==0 || sum(params$Tbl[,3])==0 || sum(params$Tbl[,4])==0) {   
 ggplot(data = params$dtlong,aes(Trial,Duration,color=Lego))+
       ggtitle(paste(params$n," Set: Power Curves (INCOMPLETE DATA SET)"))+
       theme(plot.title = element_text(size=20, hjust = .5))+
       xlab("Trials")+
       scale_y_continuous(expand=c(.1,.1),limits = c(min(params$dtlong[,3]),NA))+
       scale_x_continuous(breaks = seq(1,16,1))
} else {
  ggplot(data = params$dtlong,aes(Trial,Duration,color=Lego))+
       ggtitle(paste(params$n," Set: Power Curves"))+
       theme(plot.title = element_text(size=20, hjust = .5))+
       xlab("Trials")+
       scale_y_continuous(expand=c(.1,.1),limits = c(min(params$dtlong[,3]),NA))+
       scale_x_continuous(breaks = seq(1,16,1))+ 
       stat_smooth(method = 'nls',formula = 'y~a*x^b',method.args = list(start= c(a = 1,b=1)),se=FALSE,fullrange = TRUE,n=100)
 
}
```


```{r echo=FALSE,warning=FALSE,message=FALSE}
   ggplot(data = params$dtlong,aes(Trial,Duration,color=Lego))+
       geom_point(aes(shape = Lego),color = as.character(params$n))+
       geom_line()+
       ggtitle(paste(params$n," Set: Data and Power Curves"))+
       theme(plot.title = element_text(size=20, hjust = .5))+
       xlab("Trials")+
       scale_y_continuous(expand=c(.1,.1),limits = c(min(params$dtlong[,3]),NA))+
       scale_x_continuous(breaks = seq(1,16,1))+
       stat_smooth(method = 'nls',formula = 'y~a*x^b',method.args = list(start= c(a = 1,b=1)),se=FALSE,fullrange = TRUE,n=100)
```



## Equations

**`r as.character(params$SetTbl[1,params$n])`**: y = `r if(sum(params$Tbl[,2])==0){paste("0")} else {round(coef(nls(y1~a*x^b,data = params$DF2,start = list(a=1,b=1)))[1],4)}` x ^(`r if(sum(params$Tbl[,2])==0){paste("0")} else{ round(coef(nls(y1~a*x^b,data = params$DF2,start = list(a=1,b=1)))[2],4)}`) 

**`r as.character(params$SetTbl[2,params$n])`**: y = `r if(sum(params$Tbl[,3])==0){paste("0")} else{round(coef(nls(y2~a*x^b,data = params$DF2,start = list(a=1,b=1)))[1],4)}` x ^(`r if(sum(params$Tbl[,3])==0){paste("0")} else{round(coef(nls(y2~a*x^b,data = params$DF2,start = list(a=1,b=1)))[2],4)}`) 

**`r as.character(params$SetTbl[3,params$n])`**: y = `r if(sum(params$Tbl[,4])==0){paste("0")} else{round(coef(nls(y3~a*x^b,data = params$DF2,start = list(a=1,b=1)))[1],4)}` x ^(`r if(sum(params$Tbl[,4])==0){paste("0")} else{round(coef(nls(y3~a*x^b,data = params$DF2,start = list(a=1,b=1)))[2],4)}`) 
